Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-17 paper/paper.tex
Bypassing is an important word

In Section~\ref{sec:ppl}, we study a restricted model of Balanced RePartition, called Perfect Partition.
For that, we present a $O(k\cdot \ell)$-competitive algorithm that is optimal.
We believe that this result is an important building block on the way to an optimal algorithm for the general model.

@@

%The model is related to online
%paging~\cite{SleTar85,FKLMSY91,McGSle91,AcChNo00}.
In our
setting,
each  requests between two nodes  not in the same cluster
(i.e., inter-cluster requests) inflicts a cost until the nodes are placed in the same cluster.
This is a reminiscent of caching models \emph{with
rejection} penalty~\cite{EpImLN11,EpImLN15,Irani02}.

>>>>

In Section~\ref{sec:ppl}, we study a restricted model of Balanced RePartition, called Perfect Partition.
For that, we present a $O(k\cdot \ell)$-competitive algorithm, which is optimal.
We believe that this result is an important building block on the way to an optimal algorithm for the general model.

@@

The model is related to online
caching~\cite{SleTar85,FKLMSY91,McGSle91,AcChNo00}. In our
setting, requests can be served remotely, which is
reminiscent of caching models \emph{with
bypassing}~\cite{EpImLN11,EpImLN15,Irani02}.
